Decoding the Impact: Statistical Analysis of Factors Contributing to NFL Injuries

### 2024-04-24 paper.qmd
tests added

@@

# Display the summary of the logistic regression
result.summary()

```

@@

# Display the chi-square test results and the contingency table (if small enough)
contingency_weather_injury.shape, (chi2_weather_injury, p_value_weather_injury)

```

@@

# Display the summary of the logistic regression
result_temp.summary()

```

@@

+ https://pubmed.ncbi.nlm.nih.gov/30452873/

>>>>

from sklearn.cluster import KMeans
from sklearn.preprocessing import StandardScaler
from sklearn.decomposition import PCA

@@

# Display the summary of the logistic regression
result.summary()
```

@@

# Display the chi-square test results and the contingency table (if small enough)
contingency_weather_injury.shape, (chi2_weather_injury, p_value_weather_injury)
```

No significant association between weather conditions and types of injuries.

@@

# Display the summary of the logistic regression
result_temp.summary()
```

*Predicts whether or not an injury will occur based on temperature*

Whether the results are hot or cold, both have a significant impact on the chance of injuries.

@@

+ https://pubmed.ncbi.nlm.nih.gov/30452873/
+ https://pubmed.ncbi.nlm.nih.gov/30697503/
+ https://journals.sagepub.com/doi/pdf/10.1177/0363546518808499
